%% Note: XeLatex


%% Copyright (c) 2018-2019 Weitian LI <wt@liwt.net>
%% CC BY 4.0 License
%%
%% Résumé
%% ------
%% A short document (1-2 pages) to sum up the job-related accomplishments
%% and experience.
%%
%% Checklist
%% ---------
%% * Contact Information
%% * Work History / Experience
%% * Education
%% * Skills
%% * Summary & Objective (optional)
%% * Hobbies & Interests (optional)
%%
%% Credits
%% -------
%% * CV vs. Resume: What is the Difference? When to Use Which?
%%   https://uptowork.com/blog/cv-vs-resume-difference
%% * How to Make a Resume: A Step-by-Step Guide (+30 Examples)
%%   https://uptowork.com/blog/how-to-make-a-resume
%% * Entry-Level Resume: Sample and Complete Guide (+20 Examples)
%%   https://uptowork.com/blog/entry-level-resume-example
%%
%% Created: 2018-04-14
%%

% English version

\documentclass{resume}
%\usepackage[colorlinks,linkcolor=blue]{hyperref} 

% Adjust icon size (default: same size as the text)
\iconsize{\Large}

% File information shown at the footer of the last page
\fileinfo{%
  \faCopyright{} 2019--2022, Heng Zhang \hspace{0.5em}
  \creativecommons{by}{4.0} \hspace{0.5em}
  \githublink{https://github.com/jack-sherman01/}{resume} \hspace{0.5em}
  \faEdit{} \today
}

\name{Heng}{Zhang   }
%\keywords{BSD, Linux, Programming, Python, C, Shell, DevOps, SysAdmin}
% \tagline{\icon{\faBinoculars}} <position-to-look-for>}
% \tagline{<current-position>}
% \photo{<height>}{<filename>}
\profile{
  \mobile{191-456-99094}
  \email{hengzhang001@tongji.edu.cn}
  \github{jack-sherman01} \\
  \degree{Master in Robotics}
  \university{{\href{https://www.tongji.edu.cn/}{Tongji University (TJU)}}}
%  \birthday{1991 Sept.}
  \address{{\href{https://map.baidu.com/poi/\%E5\%90\%8C\%E6\%B5\%8E\%E5\%A4\%A7\%E5\%AD\%A6(\%E5\%98\%89\%E5\%AE\%9A\%E6\%A0\%A1\%E5\%8C\%BA)/@13494364.643751916,3648482.850872894,16.52z?uid=42e616dc8441c16b704b870e\&ugc_type=3\&ugc_ver=1\&device_ratio=2\&compat=1\&querytype=detailConInfo\&da_src=shareurl}{Shanghai, China}}}
  \home{\href{https://jack-sherman01.github.io/heng.github.io/}{Website}}\\
  % Custom information:
  % \icontext{<icon>}{<text>}
  % \iconlink{<icon>}{<link>}{<text>}
}

\begin{document}
\makeheader

%======================================================================
\sectionTitle{About Me}{\faAngellist}
%======================================================================
I am now a graduate with masters from \link{https://rail.tongji.edu.cn/}{RAIL} Lab at Tongji University (TJU), supervised by Prof. \link{https://see.tongji.edu.cn/info/1233/7519.htm} {Qijun Chen}, highly-motivated in robotics with good foundations of math and programming, proficient in data modeling and analysis, and enthusiastic about computer and the corresponding interdisciplinary subject.

I'm interested in Robot Learning, Intelligent Motion Control, Computer Vision and their applications towards Artificial General Intelligence (AGI). My current research interest focuses include:
\begin{itemize}
  \item Human-Robot Interaction (collaborative robot motion control, and drag teaching, force control);
  \item Imitation learning, robot learning and representation learning on robots;
  \item visual reasoning and the corresponding interdisciplinary directions (cognitive learning, commonsense reasoning).\\
\end{itemize}

%======================================================================
\sectionTitle{Education}{\faGraduationCap}
%======================================================================
\begin{educations}
  \education%
    {Sep. 2019}%
    [May. 2022]%
    {Tongji University (TJU)}%
    {College of Electronic and Information Engineering}%
    {Control Engineering \quad \textbf{GPA}:4.45 \quad \textbf{Rank}:1/25 \quad \textbf{IELTS}:7.0}%
    {Master's student}\\

  \separator{0.5ex}
  \education%
    {Sep. 2012}%
    [Jun. 2016]%
    {Northeast Electric Power University}%
    {School of Automation and Engineering}%
    {Automation\quad{\textbf{Honor}: Outstanding Undergraduate Thesis}}%
    {Bachelor's Degree}
    
\end{educations}


%======================================================================
\sectionTitle{Selected Publications}{\faGoogle}
%======================================================================
\begin{itemize}
\item \textbf{A Survey on Imitation Learning for Robot Manipulation} \quad [under review]\\
  \footnotesize{\textbf{Heng Zhang}, Xianyou Zhong*, Zhengang Huang, Yuan Zhao, Chengju Liu, Qijun Chen} \\
  \footnotesize{\textit{ IEEE Transactions on Cognitive and Developmental Systems @ (TCDS).}}
   
\item \textbf{Sensor-Free Method with BP Network to Achieve Drag Teaching on the 7-DOF Collaborative Robot} \quad [accepted]\\
  \footnotesize{\textbf{Heng Zhang}, Xianyou Zhong, Zhengang Huang, Chengju Liu, Qijun Chen*} \\
  \footnotesize{\textit{ China Automation Conference 2021 @ (CAC2021).}}

\item \textbf{Control Method, Device and Equipment of Collaborative Robot Drag Teaching Based on Motor Current}\quad \link{https://chn.oversea.cnki.net/KCMS/detail/detail.aspx?dbcode=SCPD\&dbname=SCPD2021\&filename=CN112894821A\&v=TjaCqUQgePwn3c33aw3kHJd\%25mmd2FmjZTayUtwOPgfOPthVU3aoB6AZpkwlCyz7qpEYXp}{[Patents]}\\
  \footnotesize{Qijun Chen, \textbf{Heng Zhang}, Chengju Liu}\\
  \footnotesize{\textit{ CN 112894821A.}}
  
\item \textbf{An indoor navigation method for Pepper robot}\quad \link{https://chn.oversea.cnki.net/KCMS/detail/detail.aspx?dbcode=SCPD\&dbname=SCPD2021\&filename=CN113029143A\&v=EY\%25mmd2BEEwMyxhcQAIQEnNmYPnHCCIfWu7KW1EmQrILR9Z\%25mmd2Bj\%25mmd2Bx14Gud3\%25mmd2BDPuHxJUUbz6}{[Patents]}\\
  \footnotesize{Chengju Liu, Qijun Chen, Liwen Lu, Jiayuan Du, \textbf{Heng Zhang}}\\
  \footnotesize{\textit{ CN 113029143A.}} 
  
\item \textbf{Motion recognition of human skeleton based on lightweight graph convolution based on channel attention}\quad \link{https://chn.oversea.cnki.net/KCMS/detail/detail.aspx?dbcode=SCPD\&dbname=SCPD2021\&filename=CN112966563A\&v=Orjxchbq030aH31bzUB\%25mmd2FZfos1lXwsLJ0ob\%25mmd2FChkqrS5\%25mmd2FV4LAUvwsj8\%25mmd2B0SqeafsLfq}{[Patents]}\\
  \footnotesize{ Chengju Liu, Ronghao Dang, Qijun Chen, \textbf{Heng Zhang}}\\
  \footnotesize{\textit{ CN113111760A.}}
  
\item \textbf{A text feature construction method based on Word2Vec and syntactic dependency tree}\quad \link{https://chn.oversea.cnki.net/KCMS/detail/detail.aspx?dbcode=SCPD\&dbname=SCPD2021\&filename=CN113111653A\&v=kIfRYxpnjYpH7kVBuJ6\%25mmd2F7Ub6AesUWPI9bNazcF7w9Ln\%25mmd2F6ppHgv7BSLRhOwHkimsd}{[Patents]}\\
  \footnotesize{ Qijun Chen, Qiuchen Wang, Chengju Liu \textbf{Heng Zhang}}\\
  \footnotesize{\textit{ CN 113111653A.}}\\
  
\item \textbf{A depth estimation method for monocular image in complex environment based on domain adaptation}\quad \link{https://chn.oversea.cnki.net/KCMS/detail/detail.aspx?dbcode=SCPD\&dbname=SCPD202102\&filename=CN113436240A\&uniplatform=NZKPT\&v=bopE9bZvDkHT59rXLk28y1Tq8\%25mmd2By\%25mmd2B\%25mmd2BQzS1\%25mmd2FqPUnoT\%25mmd2FFVqMvBxcActkJzPRcEOLqhD}{[Patents]}\\
  \footnotesize{ Qijun Chen, Mengjiao Shen, Chengju Liu, Yuchu Lu,\textbf{Heng Zhang}}\\
  \footnotesize{\textit{ CN 113436240A.}}\\
       
\end{itemize}

%======================================================================
\sectionTitle{Honors \& Awards}{\faFlagCheckered}
%======================================================================
\begin{competences}[6em]
  \comptence{Scholarship}
  {
    \textbf{1.}Innovation Scholarship for Outstanding Students,
    \textbf{2.}Second Prize Scholarship
  }
  \comptence{Contests}
  {%
    \textbf{The First Prize} 2015 Siemens Cup National Industrial Automation Challenge,
    \textbf{The First prize} Intelligent robot in the 8th Science and Technology Sports Championship of Jilin Province,
    \textbf{The Third prize} National College Students Electronic Design Competition, JiLin
  }
  \comptence{Honors}
  {%
  \textbf{1.}2022 Excellent Graduate 2022 of Tongji University.
  \textbf{2.}2022 Outstanding Graduates 2022 of Tongji University.
  \textbf{3.}2021 Winner of The Excellent Graduate Student,
  \textbf{4.}2015 Outstanding student leaders model
  }

\end{competences}




%======================================================================
\sectionTitle{Work \& Internships}{\faBriefcase}
%======================================================================
\begin{experiences}
  \experience%
    [Jul. 2020]%
    {Oct. 2020}%
    { Intern Algorithm Engineer @ China Railway Rolling stock Corp \link{https://www.crrcgc.cc/en}{(CRRC)}, Tsingtao, China}%
    [\begin{itemize}
      \item Dynamics modeling on the 7-DOF collaborative robot.
      \item Drag teaching based on a sensor-free method
    \end{itemize}]\\

  \separator{0.5ex}
  \experience%
    [Sep. 2020]%
    {Apr. 2021}%
    {Participant Student @ Project: \link{https://rail.tongji.edu.cn/\#rd12}{High performance universal robot control platform}}%
    [\begin{itemize}
      \item Motion control of 6-DOF industrial robot in joint and Cartesian space.
      \item Communication configuration based on EthaerCAT.
    \end{itemize}]\\
    
    \separator{0.5ex}
  \experience%
    [Jul. 2016]%
    {Aug. 2019}%
    {Assistant Nuclear Power Plant Design Engineer @ SMNPC at China National Nuclear Corporation \link{https://www.cnnc.com.cn/}{(CNNC)}}%
    [\begin{itemize}
      \item Instrument and Control (I\&C) system design for \link{https://baike.baidu.com/item/AP1000/543374?fr=aladdin}{AP1000} nuclear power plant.
      \item Learn design codes and specifications.
    \end{itemize}]
    
\end{experiences}


%======================================================================
\sectionTitle{Community Service}{\faChild}
%======================================================================
People are always in a community whenever and wherever, serving for community makes me have the spirit of dedication \& team-work, I am willing to make more contribution to the community.
 
\begin{competences}[6em]
  \comptence{TA}{TA in the course of ``Linear System Theory and Design''}
  \comptence{volunteer}{One-star volunteer of China Foundation for Poverty Alleviation}
  \comptence{journalist}{Student journalist in Alumni Association}
  \comptence{class president}{Serve as a class president throughout my undergraduate years}

\end{competences}




\end{document}
